{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-11-01 paper/tex/sections/discussion.tex
minor caveat rearrangement

%\textit{Other formation channels:} We also note that our findings are only the result of a single formation channel (isolated binary formation). We do not consider other channels such as dynamical formation or chemically homogeneous evolution, which could increase the detection rate and alter the parameter distributions. For instance, \citet{Kremer+2018} predict that around $21$ systems could be detected in Milky Way globular clusters with LISA, formed through dynamical formation and thus different channels can still contribute significantly to the detection rate.

\textit{Other formation channels, the Halo, globular clusters and young stellar clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo, globular clusters or young massive and open stellar clusters. \citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model. The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we again highlight the work of \citet{Kremer+2018} that investigated these rates. Similarly, we did not consider DCO formation in young massive and open stellar clusters but \citet{Banerjee+2020} finds that the LISA detection rates could be even higher than contributions from isolated binary formation.

>>>>

\textit{Other formation channels, the Halo, globular clusters and young stellar clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo, globular clusters or young massive and open stellar clusters. \citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model. The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we highlight the work of \citet{Kremer+2018} that investigated these rates. Similarly, we did not consider DCO formation in young massive and open stellar clusters but \citet{Banerjee+2020} finds that the LISA detection rates could be even higher than contributions from isolated binary formation.
